Weather Data Integration and Assimilation System\\

### 2020-02-14 method/sec_3-microservice.tex
Explained API convention more

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section \cref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} API}
\label{sebse:wdias_api}
One of the main design consideration in \acrshort{wdias} is the convention of defining the APIs. It follows the simple RESTful API, and allow users to interact with HTTP methods.

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \texttt{GET /parameter} -- Get parameters
        \item \texttt{POST /parameter} -- Create parameter
        \item \texttt{PUT /parameter/id} -- Update parameter
        \item \texttt{DELETE /parameter/id} -- Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \texttt{GET timestep} -- Get TimeSteps
        \item \texttt{POST timestep} -- Create TimeStep
        \item \texttt{PUT timestep/id} -- Update TimeStep
        \item \texttt{DELETE timestep/id} -- Delete TimeStep
    \end{itemize}
\dbc{Format others as above}
    \item location
    \begin{itemize}
        \item \emph{GET /location} - Get location points
        \item \emph{POST /location} - Create location point
        \item \emph{PUT /location/id} - Update location point
        \item \emph{DELETE /location/id} - Delete location point
        \item \emph{GET /location/regular-grid} - Get regular grids
        \item \emph{POST /location/regular-grid} - Create regular grid
        \item \emph{PUT /location/regular-grid/id} - Update regular grid
        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \emph{GET /timeseries} - Get timeseries
        \item \emph{POST /timeseries} - Create timeseries
        \item \emph{PUT /timeseries/id} - Update timeseries
        \item \emph{DELETE /timeseries/id} - Delete timeseries
    \end{itemize}
\end{itemize}

\emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
\begin{itemize}
    \item \emph{/import/json/raw}
    \item \emph{/import/ascii-grid/upload}
\end{itemize}

\emph{Export} endpoints allow to get/download data from the \acrshort{wdias} system.
\begin{itemize}
    \item \emph{/export/json/raw}
    \item \emph{/export/ascii-grid/binary}
\end{itemize}

@@

The API convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE}}  allows users to integrate new import or export modules into the system as well as add new data types.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section \cref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} API}
\label{sebse:wdias_api}
One of the main design consideration in \acrshort{wdias} is the convention of defining the \acrshort{api}. It follows a simple RESTful \acrshort{api}, and allow users to interact with HTTP methods.

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries. These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values. As an example, if it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \texttt{GET /parameter} -- Get parameters
        \item \texttt{POST /parameter} -- Create parameter
        \item \texttt{PUT /parameter/id} -- Update parameter
        \item \texttt{DELETE /parameter/id} -- Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \texttt{GET timestep} -- Get TimeSteps
        \item \texttt{POST timestep} -- Create TimeStep
        \item \texttt{PUT timestep/id} -- Update TimeStep
        \item \texttt{DELETE timestep/id} -- Delete TimeStep
    \end{itemize}
\dbc{Format others as above}
    \item location
    \begin{itemize}
        \item \emph{GET /location} - Get location points
        \item \emph{POST /location} - Create location point
        \item \emph{PUT /location/id} - Update location point
        \item \emph{DELETE /location/id} - Delete location point
        \item \emph{GET /location/regular-grid} - Get regular grids
        \item \emph{POST /location/regular-grid} - Create regular grid
        \item \emph{PUT /location/regular-grid/id} - Update regular grid
        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \emph{GET /timeseries} - Get timeseries
        \item \emph{POST /timeseries} - Create timeseries
        \item \emph{PUT /timeseries/id} - Update timeseries
        \item \emph{DELETE /timeseries/id} - Delete timeseries
    \end{itemize}
\end{itemize}

\emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
\begin{itemize}
    \item \texttt{POST import/json/raw} -- Insert Scalar/Vector timeseries data with JSON body
    \item \texttt{POST import/csv/raw} -- Insert Scalar/Vector timeseries data in CSV format
    \item \texttt{POST import/ascii-grid/upload} -- Upload set of ASCII Grid files
    \item \texttt{POST import/ascii-grid/binary} -- Upload a single ASCII Grid file
\end{itemize}

\emph{Export} endpoints allow to get/download data from the \acrshort{wdias} system.
\begin{itemize}
    \item \texttt{GET export/json/raw} -- Get Scalar/Vector timeseries data in JSON format
    \item \texttt{GET export/json/raw?start=2000-01-01\&end=2000-01-03} -- Get Scalar/Vector timeseries data in JSON format for given time period
    \item \texttt{GET export/netcdf/binary} -- Download Grid data timeseries data in \acrshort{netCDF} format
\end{itemize}

@@

As it mentioned above, other than the timeseries metadata which is the core of the data system, other module endpoints start with the module name such as import, export and extension. This allows to add new module system if required.
For import and export modules, then follows by the data format. This provide the flexibility to integrate new data format modules.
Then the endpoint name ends with the data upload/insert data type. Data can upload as a single file with binary or multiple files with upload. Or in the body of the request as raw, and need to send the required headers has mentioned by particular module.
Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.
